Testing Mac New Branch: Has 3 code for 3 tests (Chirps, Stata, NTL). Tests can be run independently through calling the file or as a set

Stata tests call files added to the testing folder

General needs: -NTL: not working yet for monthly -Output consistency: Not getting a consistent output between the NTL, Chirps, and Stata functions in terms of columns represented/number of observations

Personal to-do's -add more error checks for Stata and NTL -try with different data set

Following Fixes are important: \
\
R/Geolink.mach.R

```{r}
###Line 118
raster_objs= raster objs,
shp_fn = shp_dt
#changed to 
raster_objs= raster objs,
shp_fn = shp_fn
##explanation: used shp_fn code when it should be null, creating errors
```

R/zonalstats_plugin.R

```{r}
###Line 228 
shp_dt <- Reduce(merge, shp_dt)	
#changed to: 

#explanation: the reduce was making shp_dt null, so it breaks the code. Without it, Chirps does appear to have multiple copies of columns so need to look at alternatives 

###line 337
return (shp_dt)
##moved to line 321 ( after name_set=name_set) so shp_dt will actually be returned in the output window 
```

```{r}
###Line 325 
if (!missing(survey_dt)) {
survey_dt <- st_transform(x = survey_dt,	    
crs = st_crs(shp_dt)$wkt)

#changed to 
if (!missing(survey_dt)) {
survey_dt <- st_transform(survey_dt,
crs = st_crs(raster_objs[[1]])$input)
##explanation: error where there was no CRS recognized
```

R/download_generalhelpers

```{r}
###Line 42- added timeout 
tools::file_ext(url))
options(timeout=400)
##explanation: need timeout to be able to download larger files for NTL 
```
